---
title: "Options dans le cadre Black-Scholes"
subtitle: 'TP-2: Pricing Vanna-Volga'
date: "Version: `r format(Sys.Date(), '%d %b %Y')`"
output:
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    latex_engine: pdflatex
  word_document: default
geometry: margin=1in
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{amsmath}
- \usepackage{amsfonts}
- \usepackage{amssymb}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
The purpose of this problem set is to explore the Vanna-Volga pricing model. In this problem set, you will use the following functions:

GBSPrice: Price of a vanilla option:
\[
P = f(\text{PutCall}, S, K, T, r, b, \sigma)
\]

where:
\begin{description}
\item[PutCall] 'c' for a call, 'p' for a put
\item[$b$] cost of carry: ridk free rate $r$ less dividend yield $d$
\item[$r$] risk-free rate
\end{description}

```{r, echo=TRUE}
GBSPrice <- function(PutCall, S, K, T, r, b, sigma) {
  d1 <- (log(S/K) + (b+sigma^2/2)*T)/(sigma*sqrt(T))
  d2 <- d1 - sigma*sqrt(T)

  if(PutCall == 'c')  
    px <- S*exp((b-r)*T)*pnorm(d1) - K*exp(-r*T)*pnorm(d2)
  else
    px <- K*exp(-r*T)*pnorm(-d2) - S*exp((b-r)*T)*pnorm(-d1)

px
}
```

GBSVega: Vega ($\frac{\partial P}{\partial \sigma}$) of a Vanilla option:

```{r, echo=TRUE}
GBSVega <- function(PutCall, S, K, T, r, b, sigma) {
  d1 <- (log(S/K) + (b+sigma^2/2)*T)/(sigma*sqrt(T))
  S*exp((b-r)*T) * dnorm(d1)
}
```

# Volatility Interpolation

Given the implied volatility at three strikes, we will use the Vanna-Volga pricing method to interpolate the
volatility curve. Assume $r=0, b=0, T=1, \mbox{Spot} = 100$.

```{r, echo=TRUE}
# Benchmark data: (strike, volatility)
VolData <- list(c(80, .32), c(100, .30), c(120, .315))
```

Let's first define an array of pricing functions for the 
benchmark instruments:

```{r, echo=TRUE}
C1 <- function(vol=sigma, spot=Spot) GBSPrice(PutCall='c', S=spot, K=VolData[[1]][1], T=T, r=r, b=b, sigma=vol)

C2 <- function(vol=sigma, spot=Spot) GBSPrice(PutCall='c', S=spot, K=VolData[[2]][1], T=T, r=r, b=b, sigma=vol)

C3 <- function(vol=sigma, spot=Spot) GBSPrice(PutCall='c', S=spot, K=VolData[[3]][1], T=T, r=r, b=b, sigma=vol)

C <- c(C1, C2, C3)
```

1. Write a utility functions to compute the risk indicators,
 all by finite difference:
 
```{r, echo=TRUE}
Vega <- function(f, vol, spot=Spot) {
  # ????
}

Vanna <- function(f, vol, spot=Spot) {
  # ????
}
  
Volga <- function(f, vol) {
# ????
  }
```

Then, the calculation of vega for the three benchmark options may be performed by:

```{r, echo=TRUE}
B.vega <- sapply(1:3, function(i) Vega(C[[i]], sigma))
```

2. Compute vectors of vega, vanna, volga for the three hedge instruments

<<echo=T>>=
B.vega <- 0
B.vanna <- 0
B.volga <- 0
@

3. Choose a new strike for which we want to compute the implied volatility.


4. Compute the risk indicators for a call option struck at that strike. 
    
5. Compute the Vanna-Volga price adjustment and the corresponding implied volatility.
    

6. Wrap the above logic in a function in order to
interpolate/extrapolate the vol curve from $K=70$ to $K=130$

# Pricing a digital call

Recall that a digital call with strike $K$ pays one euro if $S_T \geq K$, and nothing otherwise.

Using the same logic as in the previous question, price a digital call, maturity $T=1$, struck at $K=105$. 
